---

library("DESeq2")
library("apeglm")
library("pheatmap")
library("tidyverse")
library("ggrepel")
library("ashr")
library("vsn")
library(gplots)
> setwd("C:/Users/username/Desktop/nekroz/")
> dir()


```{r}

ct<-read.table("necrosis.out",header = T)
treatment<-c("Control","Control","Control","Control","Subject","Subject","Subject","Subject")
Samples<-colnames(ct)[2:9]
meta<-data.frame(Samples,treatment)
View(meta)
row.names(ct)<-ct$Geneid
ct<-ct[,-1]
ct_m <- as.matrix(ct)
sumcounts <- rowSums(ct_m)
logsumcounts <- log(sumcounts,base=10)
hist(logsumcounts,breaks=100)
row.names(meta)<-meta[,1]
dds <- DESeqDataSetFromMatrix(countData = ct_m, colData = meta,design = ~ treatment)
                  verdigi uyarı hata degil...!!
View(counts(dds))
dds <- estimateSizeFactors(dds)
sizeFactors(dds)
normalized_counts <- counts(dds, normalized=TRUE)
View(normalized_counts)
write.table(normalized_counts, file="normalized_counts.txt", sep="\t", quote=F, col.names=NA)
write.csv(normalized_counts, file = "normalized_counts_necrosis.csv")
xlsx::write.xlsx(normalized_counts, file = "normalized_counts_necrosis.xlsx")

```

```{r}
keep <- sumcounts > 20
dds <- dds[keep,]
dds$condition <- relevel(dds$treatment, ref = "Control")
dds <- DESeq(dds)
resultsNames(dds)
res <- results(dds, name="treatment_Subject_vs_Control")
summary(res)
res
write.table(res, file="res.txt", sep="\t", quote=F, col.names=NA)
write.csv(res, file = "res_necrosis.csv")
xlsx::write.xlsx(res, file = "res_necrosis.xlsx")
res05 <- results(dds, alpha=0.05)
summary(res05)
res01 <- results(dds, alpha=0.01)
summary(res01)
resOrdered <- res[order(res$pvalue),]
sum(res$padj < 0.1, na.rm=TRUE)
sum(res$padj < 0.01, na.rm=TRUE)
plotMA(res, ylim=c(-7,7),cex=1)
# idx <- identify(res05$baseMean, res05$log2FoldChange)
# rownames(res05)[idx]

plotCounts(dds, gene=which.min(res$padj), intgroup="treatment")
plotCounts(dds, gene=which.max(res$padj), intgroup="treatment")

d <- plotCounts(dds, gene=which.min(res$padj), intgroup="treatment", 
                returnData=TRUE)
ggplot(d, aes(x=treatment, y=count)) +
    geom_point(position=position_jitter(w=0.1,h=0)) +
    scale_y_log10(breaks=c(25,100,400))

(ek çalışma: 
kl <- plotCounts(dds, gene=which.max(res$padj), intgroup="treatment", 
                returnData=TRUE)

ggplot(kl, aes(x=treatment, y=count)) +
    geom_point(position=position_jitter(w=0.1,h=0)) +
    scale_y_log10(breaks=c(25,100,400))
)

log_padj <- -log(res$padj,10)
log_padj[log_padj > 100] <- 100

plot(x=res$log2FoldChange,
     y=log_padj,
     pch=20,
     cex=.5,
     col=(log_padj > 10)+1, # color padj < 0.1 red
     ylab="negative log-scaled adjusted p-value",
     xlab="log2 fold changes")

boxplot(log10(assays(dds)[["cooks"]]), range=0, las=2)
```

```{r}
library("vsn")
vsd <- vst(dds, blind=FALSE)
rld <- rlog(dds, blind=FALSE)
head(assay(vsd), 20)
head(assay(vsd), 50)
head(assay(rld), 50)
ntd <- normTransform(dds)
meanSdPlot(assay(ntd))
plotPCA(vsd)


--
> ax = head(assay(vsd), 50)
> write.table(ax, file ="vsd_50_nekroz.txt", sep="\t", quote=F, col.names=NA)
> bx = head(assay(rld), 50)
> write.table(bx, file ="rld_50_nekroz.txt", sep="\t", quote=F, col.names=NA)
--
```

> library(gplots)
> mycol = colorpanel(n = 99, low = "green", mid = "black", high = "red")
> mycol = colorpanel(n = 50, low = "green", mid = "black", high = "red")
> library(pheatmap)
> pheatmap(normalized_counts, Colv = TRUE, Rowv = TRUE, col = mycol, scale = "none", legend = TRUE, trace = "row", mar = c(8,5))
> xyz = head(assay(vsd), 99)
> zyx = head(assay(rld), 99)
  > xyz = head(assay(vsd), 50)
  > zyx = head(assay(rld), 50)
> pheatmap(xyz, Colv = TRUE, Rowv = TRUE, col = mycol, scale = "none", legend = TRUE, trace = "row", mar = c(8,5))
> pheatmap(zyx, Colv = TRUE, Rowv = TRUE, col = mycol, scale = "none", legend = TRUE, trace = "row", mar = c(8,5))

veya

> pheatmap(xyz, Colv = TRUE, Rowv = TRUE, col = mycol, scale = "none", legend = TRUE, trace = "row", mar = c(8,5), pch=2, cex=1)
> pheatmap(zyx, Colv = TRUE, Rowv = TRUE, col = mycol, scale = "none", legend = TRUE, trace = "row", mar = c(8,5), pch=2, cex=1)


#> pheatmap(rld, Colv = TRUE, Rowv = TRUE, col = mycol, scale = "none", legend = TRUE, trace = "row", mar = c(8,5))

```
> write.table(resOrdered, file = "resOrdered.tsv", sep='\t')
> write.csv(resOrdered, file = "resOrdered.csv")
> xlsx::write.xlsx(resOrdered, file = "resOrdered.xlsx")

up=resOrdered[resOrdered$log2FoldChange>0,]
> write.table(up, file = "up_necrosis.tsv", sep='\t')
> write.csv(up, file = "up_necrosis.csv")
> xlsx::write.xlsx(up, file = "up_necrosis.xlsx")

down=resOrdered[resOrdered$log2FoldChange<0,]
> write.table(down, file = "down_necrosis.tsv", sep='\t')
> write.csv(up, file = "down_necrosis.csv")
> xlsx::write.xlsx(down, file = "down_necrosis.xlsx")



